---
title: "Assi-4"
author: "Sathya Prakash"
date: "2024-10-05"
output: html_document
---

```{r setup, include=FALSE}
# Load required libraries
library(boot)
library(ISLR)
set.seed(1)
```


a) Estimating standard errors using glm() function
```{r}
data(Default)

glm.fit <- glm(default ~ income + balance, data=Default, family=binomial)

summary(glm.fit)

```
(b) Writing the boot.fn() function for bootstrapping
```{r}
boot.fn <- function(data, index) {
  glm.fit <- glm(default ~ income + balance, data = data, family = binomial, subset = index)
  return(coef(glm.fit))
}

```
(c) Using the boot() function for bootstrapping
```{r}
boot(Default, boot.fn, R = 1000)
```
(d) Comment on the results
The standard errors from glm() and those obtained through bootstrapping may differ due to the nature of bootstrapping, which estimates standard errors by resampling the data.


#2LOOCV with Weekly Dataset
(a) Logistic regression with Lag1 and Lag2 as predictors
```{r}
data(Weekly)

glm.fit.weekly <- glm(Direction ~ Lag1 + Lag2, data=Weekly, family=binomial)

summary(glm.fit.weekly)

```
b) Logistic regression using all but the first observation
```{r}
glm.fit.excl1 <- glm(Direction ~ Lag1 + Lag2, data=Weekly[-1,], family=binomial)

summary(glm.fit.excl1)

```
(c) Predicting the direction for the first observation
```{r}
predict(glm.fit.excl1, Weekly[1,], type = "response") > 0.5

```
d) Implementing LOOCV manually using a for loop

```{r}
n <- nrow(Weekly)

errors <- rep(0, n)

for(i in 1:n) {
  glm.fit <- glm(Direction ~ Lag1 + Lag2, data=Weekly[-i,], family=binomial)
  pred.prob <- predict(glm.fit, Weekly[i,], type = "response")
  pred <- ifelse(pred.prob > 0.5, "Up", "Down")
  errors[i] <- ifelse(pred != Weekly$Direction[i], 1, 0)
}

loocv_error <- mean(errors)
loocv_error

```
(e) Comment on LOOCV results
The LOOCV error provides an unbiased estimate of the test error, which can be compared to other cross-validation methods like k-fold CV.
